The analogy of the cohort-equations paradigm to the compartmental epidemic models

### 2021-05-17 note/cohort.tex
adding more details to the cohort work

\title{The Paradigm of Cohort Equations for the SIR  Model With Testing and Isolation}

@@

\section{Introduction}

\section{Ideas}
This is follwoing the work of \cite{champredon2018equivalence}.

>>>>

\title{The analogy of the cohort-equations paradigm to the compartmental epidemic models}

@@

\section{Vision}
\begin{enumerate}
\item 2 frameworks of \cite{van2002reproduction}, I call it compartment framework, and \cite{champredon2018equivalence}, I call it cohort framework, can be tied together and a mechanistic approach to go from one framework to another can be constructed.

\item 
\end{enumerate}

\section{Introduction}
Notation; we use $I'$ for the cohort-framework of $dI/d\tau$ and $\dot I$ for the compartment-framework of $dI/dt$.

A simple example of this transition is the cohort analogy of a simple SIR compartmental model where $\dot I=\beta S I/N-\gamma I$. The cohort-framework is via the cohort Eq. with the following steps
step 1: write the cohort Eq. $I'=-\gamma I$ with the initial condition $I(0)=1$, 
step 2: finding the intrinsic infectiousness kernel by integrating the cohort Eq. and solving for its time evolution, thus
$k(\tau)=\beta \exp(-\gamma \tau)$.
step 3: $R$ will be the integration of the kernel. That is $R=\beta/\gamma$. 
Note that in the comartment framework, steps 2 and 3 are combined.
